Multiple Comparisons in Toolmark Evidence

### 2023-11-13 LPR/index.qmd
Update to intro

One of the common suggestions in the 2016 PCAST report across pattern disciplines in forensic science was the importance of creating huge databases of e.g. known prints and firearms to support research into matches and closest non-matches\[@pcast, fingerprints pg 11, 88, firearms pg 12\]. As researchers, we concur with this suggestion, as it is critical for developing objective algorithms and creating useful black-box studies. We have spent considerable time assembling large data sets of tool marks, bullets, and cartridge cases to support our research as well as create public resources to accelerate future research \[@csafeDataPortal\]. However, we are wary about the implications of database searches across forensic disciplines, for reasons also mentioned in the PCAST report: the necessity of understanding the random match probability for searches against these databases, in particular when using degraded evidence often found in crime scenes\[@pcast, pg 52\].

>>>>

One of the common suggestions in the 2016 PCAST report across pattern disciplines in forensic science was the importance of creating huge databases of e.g. known prints and firearms to support research into matches and closest non-matches[@pcast, fingerprints pg 11, 88, firearms pg 12]. As researchers, we concur with this suggestion, as it is critical for developing objective algorithms and creating useful black-box studies. We have spent considerable time assembling large data sets of tool marks, bullets, and cartridge cases to support our research as well as create public resources to accelerate future research [@csafeDataPortal]. However, we are wary about the implications of database searches across forensic disciplines, for reasons also mentioned in the PCAST report: the necessity of understanding the random match probability for searches against these databases, in particular when using degraded evidence often found in crime scenes[@pcast, pg 52].
